Scheeper's Meager-NWD Game and the Menger Game

### 2014-06-27 phd/dissertation/chapter3.tex
Finish draft of chapter 3

Coding strategies have been studied since the earliest days of the
Banach-Mazur game.

\begin{thm}
  (TODO: Cite the precise version of the BM game where a winning strategy
    implies a coding strategy.)
\end{thm}

@@

\begin{thm}
  $\pl F \codewin \pfgame\kappa$ implies
  $\pl O \codewin \congame{\SigmaProdR\kappa}{\vec0}$.
\end{thm}

@@

% \begin{thm}
%   Let $\cf{[\kappa]^{\leq\omega}}=\kappa$.
%   Then $\pl F \codewin \pfgame\kappa$.
% \end{thm}

% \begin{proof}
% Let $c:\kappa\to[\kappa]^{\leq \omega}$ be a funtion such that for every
% $W\in[\kappa]^{\leq\omega}$, there exists $\gamma_W<\kappa$ with
% $W\subseteq c(\gamma_W)$.

% Let $W\rest n \in [\kappa]^n$ be a subset of $W\in[\kappa]^\omega$ such that
% $W\rest n \subset W \rest (n+1)$ and $\bigcup_{n<\omega} W\rest n = W$.

% Define the coding strategy $\sigma$ as follows:
%   \[
%     \sigma(\emptyset) = \emptyset
%   \]
%   \[
%     \sigma(\<N,W\>)
%       =
%     N
%       \cup
%     (|N|+1)
%       \cup
%     \{\gamma_W\}
%       \cup
%     \bigcup_{\alpha \in N}\left(c(\alpha) \rest |N|\right)
%   \]

% Let $\<W_0,W_1,\dots\>$ be a legal attack against $\sigma$,
% $N_0=\sigma(\emptyset)$, and
% $N_{i+1}=\sigma(\<N_i,W_i\>)$. Then $\<N_0,W_0,N_1,W_1,\dots\>$ is the
% playthrough of the game coresponding to the coding strategy $\sigma$ and
% attack $a$.

% Let $\alpha\in W_i$ for some $i<\omega$. Then $\gamma_{W_i}\in N_n$ when
% $n>i$. Since $W_i\subseteq c(\gamma_{W_i})$, there exists some $n>i$ such
% that $\alpha\in c(\gamma_{W_i})\rest n$.
% Finally, we consider
%   \[
%     N_{n+1}
%       =
%     \sigma(\<N_n,W_n\>)
%       \supseteq
%     \bigcup_{\alpha\in N_n}\left(c(\alpha) \rest |N_n|\right)
%       \supseteq
%     c(\gamma_{W_i})\rest |N_n|
%   \]
% and since $|N_n|\geq n$, we may conclude $\alpha\in N_{n+1}$.
% Thus $\alpha\not\in W_j$ for $j>n$, and $\pl F$ wins the game.
% \end{proof}

%   (TODO: The above result is cute, but unnecessary due to the below.)

@@

\begin{proof}
  TODO: Fill in sketch.

  SKETCH: For each cardinal
  $\kappa$, assume $F\codewin\pfgame\lambda$ for $\lambda<\kappa$. Always
  cover the upper bound of $\pl O$'s moves if possible, or use a trick
  assuming $\cf\kappa=\omega$.
\end{proof}

\begin{cor}
  $O\codewin\congame{\SigmaProdR{\kappa}}{\vec{0}}$
  for all cardinals $\kappa$.
\end{cor}

>>>>

As an example, the existence of a winning coding strategy is necessary for the
second player to force a win the Banach-Mazur game.

\begin{thm}\label{bmcode}
  $\pl N\win\bmgame{X}$ if and only if $\pl N\codewin\bmgame{X}$
  \cite{MR817083} \cite{MR831181}.
\end{thm}

We are interested in whether the same holds for $W$ games.

@@

This game has a strong resemblance to a game defined by Scheepers in
\cite{MR1129143} in relationship to the Banach-Mazur game and studied
specifically with finite and countable sets in \cite{MR1183703}. Scheeper's
game and the results pertaining to it aren't of use here; however, they will be
referenced in a later chapter in studying a different topological game.

This game of finite and countable sets is directly applicable to the $W$
games played upon the sigma-product of real lines.

\begin{lem}
  $\pl F \codewin \pfgame\kappa$ implies
  $\pl O \codewin \congame{\SigmaProdR\kappa}{\vec0}$.
\end{lem}

@@

This lemma simplifies our notation in proving the main result. Intuitively, we
aim to show that when $\kappa$ has cofinality $\omega$, $\pl F$ can split up
the game among $\omega$-many smaller cardinals converging to $\kappa$, and
when $\kappa$ has a larger cofinality, $\pl F$ may exploit the fact that $\pl C$
may only play within some ordinal smaller than $\kappa$.

@@

\begin{proof}
  For each cardinal $\kappa$ and $\lambda<\kappa$,
  assume $\sigma_\lambda$ is a winning strategy for $\pl F$ in $\pfgame\lambda$
  such that $\sigma_\lambda(\emptyset)\supset\emptyset$ and
  $\sigma_\lambda(\<F,C\>)\supset F$.

  In the case that $\cf\kappa=\omega$, let $\<\kappa_0,\kappa_1,\dots\>$ be
  an increasing sequence of cardinals limiting to $\kappa$. Then we define
  the coding strategy $\sigma$ for $\pl F$ as follows:
    \[
      \sigma(\emptyset) = \sigma_{K_0}(\emptyset)
    \]
    \[
      \sigma(\<F,C\>)
        =
      \bigcup_{n\leq|F|}
      \sigma_{\kappa_n}(\<F\cap \kappa_n,C\cap \kappa_n\>)
    \]

  Then for each legal attack $a=\<a(0),a(1),\dots\>$ by $\pl C$ against $\sigma$
  and each $n<\omega$, the sequence
  $b_n=\<a(n)\cap \kappa_n,a(n+1)\cap \kappa_n,\dots\>$
  is a legal attack by $\pl C$ against the winning coding strategy
  $\sigma_{\kappa_n}$. It follows then that $\{a(i+n)\cap \kappa_n:i<\omega\}$
  is a point-finite cover of $\bigcup_{i<\omega}a(i+n)\cap \kappa_n$. We
  conclude that $\{a(i):i<\omega\}$ is a point-finite cover of
  $\bigcup_{i<\omega}a(i)$ and $\sigma$ is a winning strategy.

  It remains to consider the case where $\cf\kappa>\omega$. Note that now, for
  each $C\in[\kappa]^{\leq\omega}$, $C$ is bounded above in $\kappa$. So we
  define the coding strategy $\sigma$ for $\pl F$ as follows:
    \[
      \sigma(\emptyset) = \emptyset
    \]
    \[
      \sigma(\<F,C\>)
        =
      \{\sup(C)\}
        \cup
      \bigcup_{\alpha\in F}
      \sigma_{\alpha+1}(\<F\cap(\alpha+1),C\cap(\alpha+1)\>)
    \]

  Then for each legal attack $a=\<a(0),a(1),\dots\>$ by $\pl C$ against $\sigma$
  and each $n<\omega$, the sequence
  $b_n=\<a(n)\cap (\sup(a(n))+1),a(n+1)\cap (\sup(a(n))+1),\dots\>$
  is a legal attack by $\pl C$ against the winning coding strategy
  $\sigma_{\sup(a(n))+1}$. It follows then that
  $\{a(i+n)\cap (\sup(a(n))+1):i<\omega\}$
  is a point-finite cover of $\bigcup_{i<\omega}a(i+n)\cap(\sup(a(n))+1)$. We
  conclude that $\{a(i):i<\omega\}$ is a point-finite cover of
  $\bigcup_{i<\omega}a(i)$ and $\sigma$ is a winning strategy.
\end{proof}

\begin{cor}
  $\pl O\codewin\congame{\SigmaProdR{\kappa}}{\vec{0}}$
  for all cardinals $\kappa$.
\end{cor}

This leaves open the question analogous to Theorem \ref{bmcode}.

\begin{ques}
  Does $\pl O \win\congame{X}{x}$ imply $\pl O \codewin\congame{X}{x}$?
\end{ques}
